### 2019-02-18 sections/intuition.tex
tasks are predictable

Concurrency is the source of parallelism: two things are done at the same time.
%
Using tasks $t_1$ and $t_2$, the parallel combination $t_1 \And t_2$ stands for two independent tasks carried out at the same time.
For the system it does not matter if the tasks are executed by two people actually in parallel, or by one person who switches between the tasks.
All inputs sent to the combined task are interleaved into a serial stream of inputs.
The tasks are truly independent of each other, all interleavings are permitted.
Inputs to $t_1$ and $t_2$ must be prefixed by $\First$(irst) and $\Second$(econd) respectively.
This unambiguously renames the inputs, removing any source of nondeterminism.

The basic method for synchronisation in \TOP is built into the step combinator.
The task $t \Next e$ can only continue execution when two conditions are met:
Task $t$ must have a value $v$, and $e\ v$ must not evaluate to $\Fail$.
Programmers can encode arbitrary conditions in $e\ v$, which are evaluated atomically between interaction steps.
This allows a variety of synchronisation problems to be solved in an intuitive and straight-forward manner.

\TOPHAT is meant solely for implementation and does not have any form of nondeterminism.
Input events for parallel tasks are disambiguated, internal steps have a well-defined evaluation order, and internal choice is left-biased.

>>>>

The parallel combinator $\And$ introduces concurrency: Two things are done at the same time.
Let $t_1$ and $t_2$ be tasks.
The parallel combination $t_1 \And t_2$ stands for two independent tasks carried out at the same time.
For the system it does not matter if the tasks are executed by two people actually in parallel, or by one person who switches between the tasks.
The inputs sent to the component tasks are interleaved into a serial stream, which is sent to the parallel combinator.
We assume that such a serialization is always possible.
The tasks are truly independent of each other, all interleavings are permitted.
The environment must prefix events to $t_1$ and $t_2$ by $\First$ (first) and $\Second$ (second) respectively.
This unambiguously renames the inputs, removing any source of nondeterminism.

With concurrency comes the need for synchronisation, in situations where only some but not all interleavings are desired.
The basic method for synchronisation in \TOPHAT is built into the step combinator.
The task $t \Next e$ can only continue execution when two conditions are met:
Task $t$ must have a value $v$, and $e\ v$ must not evaluate to $\Fail$.
Programmers can encode arbitrary conditions in $e\ v$, which are evaluated atomically between interaction steps.
This allows a variety of synchronisation problems to be solved in an intuitive and straight-forward manner.

\Citet{books/Hoare85CSP} states that nondeterminism is only ever useful for \emph{specifying} systems, never for implementing them.
\TOPHAT is meant solely for implementation and does not have any form of nondeterminism.
Input events for parallel tasks are disambiguated, internal steps have a well-defined evaluation order, and internal choice is left-biased.
